article title

### 2022-12-15 article.tex
Add blocking
Add items for display
Change variables names

Here is a request to fill in \gls{dependentvariable} and \glspl{dependentvariable}.

For dual abbreviations and glossary terms, \gls{anome}.

\gls{fixedeffectsmodel}

\gls{randomeffectsmodel}

\gls{expectedmeansquares}

\gls{mixedeffectsmodel}

>>>>

Here is a request to fill in \gls{endog}, \glspl{endog}, \gls{exog}, and \glspl{exog}.

For dual abbreviations and glossary terms, \gls{aad}, \gls{mad}, \gls{mae}, \gls{mse}, \gls{rmse}, and \gls{anome}.

\gls{interaction}
